Gray Box Optimization using the Parameter-less Population Pyramid

### 2015-01-20 Gray Box Optimization using the Parameter-less Population Pyramid/main.tex
Abstract draft

\maketitle
\begin{abstract}
%Maximum 200 Words
TODO
\end{abstract}

>>>>

\maketitle
\begin{abstract}
%Maximum 200 Words

For many challenging problems, the non-linear relationships between variables
are known and bounded. Previous work has developed local search operators
which require a linear factor less time than black box methods. Furthermore,
this Hamming-Ball Hill Climber is capable of efficiently finding $r$-bit local optima.
In this paper we extend this operator to perform efficient global optimization.
We create a simple memetic algorithm to demonstrate how even trivial
extensions can improve search results. We then modify the Parameter-less
Population Pyramid (P3), shown to be highly effective for black box optimization,
to leverage the additional information available in the gray box domain.

We provide experimental evidence on both NKq-Landscapes and Ising Spin Glasses
that Gray Box P3 is effective at finding the global optima even for problems with
thousands of variables. This capability is complemented by its efficiency, with
running time and memory usage decreased by a linear factor from Black Box P3.
On NKq this results in a x374 speedup for problems with at least 1000 variables.
While local search introduces a parameter, we experimentally show this parameter
can likely be fixed to 1 without significant loss in search quality.

\end{abstract}
